Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-25 documentation/paper.tex
Updated all supervised learning tables except summary

\begin{center}
    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 95\% & 99\% & 85\% & 0.44 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1533824431_epoch30.json
        \hline
        0.003 & 0 & 48 & 5 & 3 & 96\% & 99\% & 89\% & 0.41 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533825716_epoch43.json
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 93\% & 98\% & 83\% & 0.50 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1533828588_epoch27.json
        \hline
        0.001 & 0 & 48 & 5 & 3 & 95\% & 98\% & 87\% & 0.48 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533832229_epoch16.json
        \hline
        0.001 & 0.25 & 48 & 3 & 6 & 93\% & 94\% & 91\% & 0.62 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters48_kernel_size3_convolutional_layers_per_group6time1533834812_epoch30.json
        \hline
        0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 97\% & 91\% & 0.49 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group6time1533849077_epoch45.json
        \hline
    \end{tabular}

    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ without $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 91\% & 0.61 \\
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 91\% & 0.65 \\
        \hline
        0.001 & 0.25 & 24 & 3 & 3 & 91\% & 0.66 \\
        \hline
        0.001 & 0.5 & 48 & 5 & 3 & 88\% & 0.73 \\
        \hline
        0.0003 & 0 & 48 & 5 & 6 & 78\% & 0.95 \\
        \hline
        0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 0.92 \\
        \hline
    \end{tabular}
\end{center}

@@

@@

Very interestingly, $FourierMLP(\beta_{8})$ performed better than either $FourierMLP(PosCor(\beta_{8}), \chi)$ or \\ $FourierMLPWithPos(\beta{8}, \chi)$, which produced accuracy values of 97\% and 95\%, respectively.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Neural networks trained on Fourier transforms with $WallCut(D)$.} \label{fft_wall_cuts}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
            \hline
            $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
            \hline
            $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 0.57 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 0.53 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 0.56 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 0.64 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 0.65 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$FourierMLPWithPos(\beta{N})$ trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 92\% & 0.63 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0 & 0 & 3 & 95\% & 0.49 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0 & 2 & 96\% & 0.47 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0 & 2 & 97\% & 0.47 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.25 & 2 & 95\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 2 & 94\% & 0.53 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

@@

\begin{center}
    \captionof{table}{Performance of $ImageConv(\iota)$ configurations, trained without $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0 & 0.5 & 4 & 3 & 77\% & 1.01 \\
        \hline
        0 & 0.25 & 4 & 3 & 85\% & 0.95 \\
        \hline
        0.01 & 0.25 & 4 & 3 & 66\% & 0.97 \\
        \hline
        0.003 & 0.25 & 4 & 3 & 69\% & 0.97 \\
        \hline
        0.01 & 0.25 & 12 & 3 & 66\% & 0.98 \\
        \hline
        0.01 & 0.5 & 12 & 3 & 68\% & 0.99 \\
        \hline
    \end{tabular}
\end{center}

@@

>>>>

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 3 & 95\% & 99\% & 94\% & 0.44 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1533824431_epoch30.json
            \hline
            0.003 & 0 & 48 & 5 & 3 & 96\% & 99\% & 96\% & 0.41 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533825716_epoch43.json
            \hline
            0.003 & 0.5 & 24 & 5 & 3 & 93\% & 98\% & 92\% & 0.50 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1533828588_epoch27.json
            \hline
            0.001 & 0 & 48 & 5 & 3 & 95\% & 98\% & 95\% & 0.48 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533832229_epoch16.json
            \hline
            0.001 & 0.25 & 48 & 3 & 6 & 93\% & 94\% & 97\% & 0.62 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters48_kernel_size3_convolutional_layers_per_group6time1533834812_epoch30.json
            \hline
            0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 97\% & 97\% & 0.49 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group6time1533849077_epoch45.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 3 & 91\% & 95\% & 78\% & 0.61 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532800009_epoch78.json
            \hline
            0.003 & 0.5 & 24 & 5 & 3 & 91\% & 95\% & 78\% & 0.65 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1532813246_epoch49.json
            \hline
            0.001 & 0.25 & 24 & 3 & 3 & 91\% & 88\% & 84\% & 0.66 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532825383_epoch88.json
            \hline
            0.001 & 0.5 & 48 & 5 & 3 & 88\% & 92\% & 73\% & 0.73 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1532837124_epoch0.json
            \hline
            0.0003 & 0 & 48 & 5 & 6 & 78\% & 76\% & 56\% & 0.95 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532846835_epoch63.json
            \hline
            0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 67\% & 53\% & 0.92 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532863869_epoch10.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

It is notable that recall is much, much poorer when wall cuts are applied. It seems there are more neutron events that show alpha-like audio signatures in the events near the walls, possibly due to resonance.

@@

Very interestingly, $FourierMLP(\beta_{8})$ performed better than either $FourierMLP(PosCor(\beta_{8}), \chi)$ or \\ $FourierMLPWithPos(\beta{8}, \chi)$, which produced accuracy values of 96\% and 97\%, respectively.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Neural networks trained on Fourier transforms with $WallCut(D)$.} \label{fft_wall_cuts}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Acc & Prec & Recall & CWSD \\
            \hline
            $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 96\% & 98\% & 97\% & 0.42 \\
            % ../experimental_data/validation_results/2018_07_16_banded_frequency_validation_passing_weighted_3_times.json
            \hline
            $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 100\% & 98\% & 0.29 \\
            % ../experimental_data/validation_results/2018_07_17_banded_frequency_not_position_corrected/banded_low_resolution_time1531831056_epoch249.json
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 100\% & 92\% & 0.44 \\
            % ../experimental_data/validation_results/2018_07_17_banded_frequency_not_position_corrected_with_position_input/banded_low_resolution_time1531837503_epoch18.json
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 98\% & 98\% & 0.43 \\
            % ../experimental_data/validation_results/2018_07_18_banded_frequency_25\%_dropout/banded_low_resolution_time1531922044_epoch154.json
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 99\% & 92\% & 0.54 \\
            % ../experimental_data/validation_results/2018_07_20_20_bands/high_resolution_frequency_time1532105605_epoch90.json
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 99\% & 93\% & 0.52 \\
            % ../experimental_data/validation_results/2018_07_20_20_bands_no_regularization/high_resolution_frequency_time1532113464_epoch172.json
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 98\% & 90\% & 0.57 \\
            % ../experimental_data/validation_results/2018_07_20_40_bands/high_resolution_frequency_time1532107386_epoch101.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 94\% & 93\% & 0.53 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0_l2_lambda0.0003_hidden_layers3_time1533922958_epoch133.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 96\% & 89\% & 0.56 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.25_l2_lambda0.001_hidden_layers3_time1533924257_epoch115.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 91\% & 91\% & 0.64 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.5_l2_lambda0.001_hidden_layers2_time1533925299_epoch169.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 90\% & 93\% & 0.65 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.5_l2_lambda0.01_hidden_layers3_time1533925799_epoch91.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$FourierMLPWithPos(\beta{N})$ trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Acc & Prec & Recall & CWSD \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 92\% & 93\% & 77\% & 0.63 \\
            % ../experimental_data/validation_results/2018_07_20_no_wall_cuts/high_resolution_frequency_time1532116206_epoch111.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0 & 0 & 3 & 95\% & 89\% & 95\% & 0.49 \\
            % ../experimental_data/validation_results/2018_07_24_high_resolution_frequency_grid_search/high_res_grid_search_dropout0_l2_lambda0_hidden_layers2_time1532446602_epoch210.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0 & 2 & 96\% & 95\% & 93\% & 0.47 \\
            % ../experimental_data/validation_results/2018_07_24_high_resolution_frequency_grid_search/high_res_grid_search_dropout0_l2_lambda0.001_hidden_layers1_time1532448014_epoch149.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0 & 2 & 97\% & 93\% & 98\% & 0.47 \\
            % ../experimental_data/validation_results/2018_07_24_high_resolution_frequency_grid_search/high_res_grid_search_dropout0_l2_lambda0.01_hidden_layers1_time1532449765_epoch108.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.25 & 2 & 95\% & 97\% & 86\% & 0.54 \\
            % ../experimental_data/validation_results/2018_07_24_high_resolution_frequency_grid_search/high_res_grid_search_dropout0.25_l2_lambda0.01_hidden_layers1_time1532454347_epoch122.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 2 & 94\% & 95\% & 86\% & 0.53 \\
            % ../experimental_data/validation_results/2018_07_24_high_resolution_frequency_grid_search//high_res_grid_search_dropout0.5_l2_lambda0.01_hidden_layers1_time1532459365_epoch243.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

Unlike with the raw waveform, recall varies relatively little when wall cuts are applied.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Performance of $ImageConv(\iota)$ configurations, trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0 & 0.5 & 4 & 3 & 77\% & 52\% & 31\% & 1.01 \\
            % ../experimental_data/validation_results/2018_07_26_image_classification_fixed_loading/image_time1532640532_epoch8.json
            \hline
            0 & 0.25 & 4 & 3 & 85\% & 40\% & 38\% & 0.95 \\
            % ../experimental_data/validation_results/2018_07_26_image_classification_less_dropout_more_epochs/image_time1532615758_epoch164.json
            \hline
            0.01 & 0.25 & 6 & 3 & 68\% & 68\% & 100\% & 0.98 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.25_convolutional_layers_per_group2time1532895825_epoch2.json
            \hline
            0.003 & 0.25 & 9 & 3 & 68\% & 68\% & 100\% & 0.98 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.003_dropout0.25_convolutional_layers_per_group3time1532895118_epoch3.json
            \hline
            0.01 & 0.25 & 12 & 3 & 68\% & 68\% & 100\% & 0.97 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.25_convolutional_layers_per_group4time1532896126_epoch0.json
            \hline
            0.01 & 0.5 & 12 & 3 & 68\% & 68\% & 100\% & 0.99 \\
            % ../experimental_data/validation_results/2018_07_29_image_grid_search/image_grid_search_l2_lambda0.01_dropout0.5_convolutional_layers_per_group4time1532898944_epoch1.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

The 100\% recall statistics are not due to high classification accuracy, but rather due to the network making predictions less than 0.5 for all examples of both classes.
